---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# backCUSUM

<!-- badges: start -->
<!-- badges: end -->

The goal of backCUSUM is to provide functionality to apply the methods developed in the paper "[Backward CUSUM for Testing and Monitoring Structural Change](https://arxiv.org/abs/2003.02682)" by [Sven Otto](https://www.svenotto.com) and [Jörg Breitung](https://wisostat.uni-koeln.de/en/institute/professors/breitung). The repository also provides code to replicate all simulation results in this paper.

## Installation

You can install the package using the following command:

``` r
library('devtools')
install_github("ottosven/backCUSUM/backCUSUM")
```

## Example

This is a basic example to reproduce Figure 2 of the paper:

```{r example}
library(backCUSUM)
RNGkind("L'Ecuyer-CMRG")
set.seed(42)
T <- 100
breakpoint <- floor(3*T/4)
beta1 = 0
beta2 = 1
u <- rnorm(T,0,1)
y <- c(rep(beta1,breakpoint), rep(beta2,T-breakpoint)) + u
Qt <- Q.detector(y~1)
BQt <- BQ.detector(y~1)
wt <- get.recresid(y~1)
```

This is the plot:

```{r pressure, echo = FALSE}
par(mfrow=c(1,2))
plot(Qt, lwd = 2, type='l', col='blue', xlab = "", ylab = expression(), ylim=c(-2, 3.2), main='Forward CUSUM')
mtext(text = "time",side = 1, line = 2)
lines((0.948*(1+2*(1:T)/T)), lty=2, col='red', lwd=1)     # critical boundaries for alpha = 0.0001
lines(wt, col='grey', lwd = 1)
lines( x=c(1,100), y=c(0, 0), col='black', lwd=1, lty = 2)
plot(BQt, lwd = 2, type='l', col='blue', xlab = "", ylab = expression(), ylim=c(-2, 3.2), main='Backward CUSUM')
mtext(text = "time",side = 1, line = 2)
lines((0.948*(1+2*(T:1)/T)), lty=2, col='red', lwd=1)
lines(wt, col='grey', lwd = 1)
lines( x=c(1,100), y=c(0, 0), col='black', lwd=1, lty = 2)
par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("bottom", c("detector statistic", "linear boundary (5%)", "recursive residuals"), horiz = TRUE, bty = "n", cex=1 , col = c('blue', 'red', 'grey'), lty=c(1, 2, 1), lwd = c(2, 1, 1) )

```
